Sequential rank agreement methods for comparison of ranked lists

### 2016-03-31 latex/paper.Rnw
more asymptotic

The agreement of the lists regarding the rank given to an item $X_p$ can be
measured by
\begin{equation}
  A(X_p) = f(R_1(X_p), \ldots, R_L(X_p))
\end{equation}
for a measurable non-negative real-valued distance function $f$.
For an integer $1\le d\le P$ we define the unique set of items found
by merging the first $d$ elements of each of the $L$ lists, i.e., the
set of items ranked less than or equal to $d$ in any of the lists:
\begin{equation}
S_d = \{R_l^{-1}(r) ; r \leq d, l = 1, \ldots, L \},
\end{equation}
which is exemplified in Panel (c) of Table \ref{tab:example}.
We then define the \emph{sequential rank agreement} as pooled expected agreement of the items
found in the set $S_d$:
\begin{equation}
\textrm{sra}(d)= \frac{\sum_{\{p \in S_d\}}(L-1)\E[A(X_p)]}{(L-1)|S_d|}\label{def:sra}
\end{equation}
where $|S_d|$ refers to the cardinality of the set $S_d$, and the expectation
is taken with respect to the distribution of the rankings of $X_p$ accross the $L$ lists.
Values of \textrm{sra} close to zero suggests that the lists agree while larger
values suggest disagreement. Just like in method comparison studies we
prefer smaller limits of agreement because that means that the
differences between the methods is small. If the ranked lists are
identical then the value of sequential rank agreement will be zero for
all depths $d$.

@@

\begin{corollary}
For fixed $q$ it follows from theorem \ref{thm:consistency}
  $\widehat{d^\ast_L}(q) \overset{P}{\longrightarrow} d^\ast(q)$
\begin{proof}
 hej
\end{proof}
\end{corollary}

@@

The overlap among $L$ lists observed until depth $d$ is defined as the
proportion of items that are found in all $L$ lists compared to the
possible number of items found in all lists observed until depth $d$:
\begin{equation}
  O(d) = \frac{| \cap_{l=1}^L \{R_l^{-1}(r); r\leq d \} |}{d}. \label{def:overlap}
\end{equation}
Typically the overlap is only considered for pairwise comparisons
\citep{Bar-Ilan2006,Boulesteix2009} but formula \eqref{def:overlap}
is easily extended to the situation where $L>2$ as shown above.

>>>>

The agreement of the lists regarding the rank given to an item $X_p$ can be
measured by
\begin{equation}
  A(X_p) = f(R_1(X_p), \ldots, R_L(X_p))
\end{equation}
for a measurable non-negative real-valued distance function $f$.
For an integer $1\le d\le P$ we define the unique set of items found
by merging the first $d$ elements of each of the $L$ lists, i.e., the
set of items ranked less than or equal to $d$ in any of the lists:
\begin{equation}
S_d = \{R_l^{-1}(r) ; r \leq d, l = 1, \ldots, L \},
\end{equation}
which is exemplified in Panel (c) of Table \ref{tab:example}.
We then define the \emph{sequential rank agreement} as the weighted expected agreement of the items
found in the set $S_d$: [FIX: we have talked about this before, but does that redundant (L-1) factor help wrt interpretation?]
\begin{align}
\textrm{sra}(d)&= \frac{\sum_{\{p \in S_d\}}(L-1)\E[A(X_p)]}{(L-1)|S_d|}\label{def:sra}\\
   &= \sum_{\{p \in S_d\}}|S_d|^{-1} \E[A(X_p)]
\end{align}
where $|S_d|$ refers to the cardinality of the set $S_d$, and the expectation
is taken with respect to the distribution of the rankings of $X_p$ accross the $L$ lists.
Values of \textrm{sra} close to zero suggests that the lists agree while larger
values suggest disagreement. Just like in method comparison studies we
prefer smaller limits of agreement because that means that the
differences between the methods is small. If the ranked lists are
identical then the value of sequential rank agreement will be zero for
all depths $d$.

@@

\begin{corollary}
For fixed $q$ it follows from theorem \ref{thm:consistency} that
$\widehat{d^\ast_L}(q) \overset{P}{\longrightarrow} d^\ast(q)$
for $L \rightarrow \infty$.
\begin{proof}
 hej
\end{proof}
\end{corollary}

@@

The overlap among $L$ lists observed until depth $d$ is defined as the
proportion of items that are found in all $L$ lists compared to the
possible number of items found in all lists observed until depth $d$:
\begin{equation}
  O(d) = \frac{| \cap_{l=1}^L \{R_l^{-1}(r); r\leq d \} |}{d}. \label{def:overlap}
\end{equation}
Typically the overlap is only considered for pairwise comparisons
\citep{Bar-Ilan2006,Boulesteix2009} but formula \ref{def:overlap}
is easily extended to the situation where $L>2$ as shown above.
